Nail: A practical interface generator for data formats

### 2014-05-02 paper/osdi14/impl.tex
another type

Security exploits often rely on raw inputs being present in memory, for example to include
shell-code or crafted stack frames for ROP-attacks in padding fields\cite{shotgun-parser} or the
application executing a controlled sequence of heap allocations and de-allocations to place
specific data at predictable addresses\cite{jp-advanced, vudo-malloc}. Because the rest of the
application or even Nail's generated code may contain memory corruption bug, Nail
carefully handles memory allocations as defense-in-depth to make exploiting such vulnerabilities harder.

>>>>

Security exploits often rely on raw inputs being present in memory, for example to include
shell-code or crafted stack frames for ROP-attacks in padding fields\cite{shotgun-parser} or the
application executing a controlled sequence of heap allocations and de-allocations to place
specific data at predictable addresses\cite{jp-advanced, vudo-malloc}. Because the rest of the
application or even Nail's generated code may contain memory corruption bugs, Nail
carefully handles memory allocations as defense-in-depth to make exploiting such vulnerabilities harder.
